fig4

### 2020-03-01 analysis/figure-4.Rmd
second manipulatino figure
new output for plotnplay.R : :

```{r setup, include=FALSE}
library(tidyverse)
library(cowplot)

@@

@@

>>>>

# Figure 4

```{r setup, include=TRUE}
library(tidyverse)
library(cowplot)

@@

candidategenes <- c("PRL", "PRLR" ,  "AVPR1B" , "MYC" ,  
                "MAP2KA", "MSH" ,   "PALB2" , "BRCA1", 
                "OXT", "ESR1", "ESR2", "CISH", 
                "POU2F1", "RAP1GAP", "CEBPB","ARHGAP32"
                )

returnvsds <- function(whichgenes){

  df  <- allvsd %>%
    filter(gene %in% whichgenes) %>%
    dplyr::mutate(sextissue = sapply(strsplit(file_name, '_vsd.csv'), "[", 1)) %>%
    dplyr::mutate(sextissue = sapply(strsplit(sextissue, '../results/DEseq2/'), "[", 2)) %>%
    dplyr::mutate(sex = sapply(strsplit(sextissue, '\\_'), "[", 1),
                tissue = sapply(strsplit(sextissue, '\\_'), "[", 2),
                treatment = sapply(strsplit(samples, '\\_'), "[", 4)) %>%
    dplyr::mutate(treatment = sapply(strsplit(treatment, '.NYNO'), "[", 1)) %>%
    dplyr::select(sex, tissue, treatment, gene, samples, counts)

  df$treatment <- factor(df$treatment, levels = alllevels)
  print(head(df))
  return(df)
}

candidatevsd <- returnvsds(candidategenes)

@@

```{r savefiles}
write.csv(candidatevsd, "../../musicalgenes/data/candidatecounts.csv")
```
